Describing demographic models is hard

### 2020-05-19 paper.tex
ghost clarification

Fortunately, the effect of this additional 'ghost' population are subtle. Population sizes and structure since the time of
the split are unaffected, so that differences in expected $F_{ST}$ are negligible between
the correct and incorrect model. However, the presence of the ghost population increases
the effective population size and thus affects the distribution of older $T_{MRCA}$ and the expected 
heterozygosity in each of the three populations by up to $4\%$ (Fig.~\ref{fig:ooa_stats}C-G).

>>>>

Fortunately, the effect of this additional, 'ghost' population are subtle. Population sizes and structure since the time of
the split are unaffected, so that differences in expected $F_{ST}$ are negligible between
the correct and incorrect model. However, the presence of the ghost population increases
the effective population size and thus the distribution of $T_{MRCA}$ and the expected 
heterozygosity in each of the three populations by up to $4\%$ (Fig.~\ref{fig:ooa_stats}C-G).
